SIMITAR: realistic and autoconfigurable traffic generation

### 2017-12-02 Docs/PaperSimitar/body.tex
paper

%Emerging technologies such as SDN and NFV are  drastically changing  computer networks. But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads. Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect an even larger impact over over virtualized middle-boxes should be even larger, due the virtualization layer extra overhead. Also, we have the flow-based ofperation of  SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller. The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table. Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject. 
Emerging technologies such as SDN and NFV are  drastically changing  computer networks. But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}, since hardware solutions  have a much more predictable behavior. There is a demand for more reliable methods to ensure the Service Layer Agreements, over different types of loads. We can expect an even larger impact over over virtualized middle-boxes should be even larger compared to dedicated hardware devices, due the virtualization-layer extra overhead. Along with that, on Software Defined Networks we have the flow-based operation. Each new flow arriving on an SDN switch demands an extra communication between it and the controller, wich may create a boobleneck. The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table. Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.

@@

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more. Traffic generators are commonly classified into four different groups\cite{do-you-trust}: application-level, flow-level, packet-level and multi-level traffic generators.

\textbf{Application-level traffic generators}: they try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool. That means, the behavior of the output may change according to what packets have arrived in the network interface}. As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services. The behavior of such applications is, in general, based on request-response exchanges models.

\textbf{Flow-level traffic generators}: they are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}. Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.

\textbf{Packet-level traffic generators}: most traffic generators available fall in this class. They are able to craft packets and inject into the network, and controll features like inter departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}. \cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators. Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, are  able to read packet capture files (\textit{pcap} files), and inject copies on a network interface. Model-based generators, such D-ITG \cite{ditg-paper}, TG\cite{web-tg}, may have PS and IDT configured by the user. They can configure IDT  either by constant values (defining the packet rate or bandwidth) or by stochastic models. Maximum throughput engines like Ostinato and Seagull are tools that the main goal is to perform end-to-end stress testing. Are included in this category generators that are able to craft packets from the link layer, like Brute, KUTE, and pktgen.

\textbf{Multi-level traffic generators}: its proposal is to take into account existing interaction among each layer of the network stack, to create background network traffic as close as possible from reality. The most relevant tool of this class is Swing \cite{swing-paper}. Swing take into account many points of each layer, using an approach based on randomness and responsiveness \cite{swing-paper}. That means, it uses packet-sizes and inter packet times stochastic models, but also take into account flow and application layer behavior. Swing is able to model things like\cite{swing-paper}:

\begin{itemize}

	\item User behavior: Number of request and responses, time between requests and responses;

	\item Request and Responses: number of connections, time between start of connections;

	\item Connection: Number of request and responses per connection, applications modeling (HTTP, P2P, SMTP), transport protocols TCP/UDP based on the application, response sizes, request sizes, user think between exchanges on a connection;

	\item Packet: packet size (Maximum transmission unit), IP addresses, (MTU), bit rate and packet arrival distribution,

	\item Link: link Latency Delay, loss rates.

\end{itemize}

Swing take as input collected \textit{pcap} files. Botta at al. \cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers. Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}. The authors Vishwanat et al. \cite{swing-paper} cite that they have generated traces of about of 200 Mbps, about the same result found by \cite{legotg-paper}. In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.

Application level traffic generators may be realistic from a server operation system perspective, but are not able to represent real complex scenarios. Replay engines such as  TCPreplay and TCPivo have some limitation. First, they usually do not replicate the same inter-packet times form the original trace, just creates a constant bandwidth traffic. They also requere storage of \textit{pcap} files, wich may become huge for  long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and limited sources.  Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do. So, there is no simple way for the user to create an synthetic realistic traffic scenario.

We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. Many of the listed traffic generators provides their own high-level API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

@@

Therefore we have a large variety open-source tools available for custom traffic generation. But reproducing a realistic traffic scenario is a hard question. Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}. But usually this is not the goal of the project, so the researcher or the them have scarce time available to work over it. Since it is usually is not the main goal of the project, but just a mean many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.   Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation. Since it usually is not the goal of the research, but a mean.

For this gap, there are some sollutions on the open source community. Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. This is clearly a hard task\cite{legotg-paper}, and an error prone activity. Again, we fall in the same problem a complex task that usually is not the goal of the project.

Another issue is the large variety of tools, and different methods of configuration and limitations. To create a custom traffic, a user must read large manuals, and custom-design scripts. One of our bigger proposals is create a tool able to automatically do this processes. So The user may design his custom traffic by creating his own Compact Trace Descriptor, and create a traffic using many different tools, like Ostinato, D-ITG, Iperf, but not caring about how to proper configure each of them.

@@

To meet the requirements presented in the section ~\ref{sec:introduction}, we will define our solution, and how it works. SIMITAR architecture is presented in the figure~\ref{fig:architecture}. It is composed of four components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem. We describe each part below.

\begin{figure}[ht!]
        \centering
        \includegraphics[height=2.7in]{figures/architecture-diagram}
        \caption{Architecture of SIMITAR}
    \label{fig:architecture}
\end{figure}

@@

It has a data structure we developed called \textit{OrderedSet}. A set is a list of elements with no repetition but does not keep track of the insertion order. Our OrderedSet does. Also, it makes use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}. The listed header fields are inputs for a hash function, and its value is set on the ordered set which returns its order (index on the \textit{OrderedSet}). The index value is chosen as a packet flowID.

@@

The database stores the collected raw data from the traces for further analysis. The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.  We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our purposes. It is simple and well-suitable for an amount of data smaller than terabytes. In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the flowID calculated by the sniffer component.

@@

At the \textbf{session layer}, we use a deterministic approach for evaluating file transference time and times between files: ON/OFF times sequence of packet trains. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the ON times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Also in the case of just one packet, the ON time would be zero. So setting a minimum acceptable time to solve these issues. The OFF times, on the other hand, are defined by the constant \texttt{session\_cut\_time} \footnote{In the code it is called \texttt{DataProcessor::m\_session\_cut\_time} }. If the time between two packets of the same flow is larger than \texttt{session\_cut\_time}, we consider them belonging to a different file, so this time is a session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} for the \texttt{session\_cut\_time}: 30 seconds. The control of ON/OFF periods in the traffic generation is made by the \textit{Flow Generator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Validation}\label{sec:validation}

>>>>

%> SDN e NFV
Emerging technologies such as SDN and NFV are  drastically changing  computer networks. But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}, since hardware solutions  have a much more predictable behavior. There is a demand for more reliable methods to ensure the Service Layer Agreements, over different types of loads. We can expect an even larger impact over over virtualized middle-boxes should be even larger compared to dedicated hardware devices, due the virtualization-layer extra overhead. Along with that, on Software Defined Networks we have the flow-based operation\cite{sdn-survey}. Each new flow arriving on an SDN switch demands an extra communication between it and the controller, wich may create a boobleneck. The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table. Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject. 
%Emerging technologies such as SDN and NFV are  drastically changing  computer networks. But enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads. Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect an even larger impact over over virtualized middle-boxes should be even larger, due the virtualization layer extra overhead. Also, we have the flow-based ofperation of  SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller. The SDN switches have a flow-oriented operation, since it check each new packet in an flow-match table. Therefore an performance measurement must use a traffic with the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How virtualized network functions,  virtualized middle-boxes and SDN switches and cotrollers will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is an important study subject.

@@

%> sobre open-source traf gen
The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, each of them wiht diferent methods of traffic generation and enabling the controll of  different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, packet train periods, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more. Traffic generators are commonly classified into four different groups, according to its layer of operation\cite{do-you-trust}: application-level, flow-level, packet-level and multi-level traffic generators.

%> Applucation-level
\textbf{Application-level traffic generators} try to emulate the behavior of network applications, simulating real workloads stochastically and/or responsively \footnote{Responsiveness refers to the property of capacity of response over time of the workload tool. That means, the behavior of the output may change according to what packets have arrived in the network interface}. As examples we have Surge\cite{surge-paper} able to emulate the behavior of web clients and services.

%> Flow-level
\textbf{Flow-level traffic generators} are able to configure and reproduce features of flows\cite{do-you-trust}\cite{sourcesonoff-paper}, such as number of flows and flow duration, start times distributions, and temporal (diurnal) traffic volumes\cite{do-you-trust}. Harpoon \cite{harpoon-paper} is able to extract these parameters from Cisco NetFlow data, collected from live routers.

%> Packet-level
\textbf{Packet-level traffic generators} is the most common  traffic generators class available. They are able to craft packets and inject into the network, and controll features like inter departure times (IDT), packet size(PS), throughput and packets per second\cite{validate-trafficgen}. \cite{validate-trafficgen} classify them as replay engines, maximum throughput generators, and model based generators. On the other hand, offer the control for just a single flow each time, and if available will require scripting. Traffic Replay engines, such TCPreplay\cite{web-tcpreplay}, are  able to read packet capture files (\textit{pcap} files), and inject copies on a network interface. Model-based generators, such D-ITG \cite{ditg-paper}, TG\cite{web-tg}, may have PS and IDT configured by the user. They can configure IDT  either by constant values (defining the packet rate or bandwidth) or by stochastic models. Maximum throughput engines like Ostinato and Seagull are tools that the main goal is to perform end-to-end stress testing. Are included in this category generators that are able to craft packets from the link layer, like Brute, KUTE, and pktgen.

%> multi-level
\textbf{Multi-level traffic generators} have the porpose of  take into account existing interaction among each layer of the network stack, to create network traffic as close as possible from reality. The most relevant open-source  tool of this class is Swing \cite{swing-paper}. Swing take into account many points of each layer, using an approach based on randomness and responsiveness \cite{swing-paper}. That means, it uses packet-sizes and inter packet times stochastic models, but also take into account flow and application layer behavior. Swing is able to model things like\cite{swing-paper}: 
\begin{itemize}
	\item User behavior: Number of request and responses, time between requests and responses;
	\item Request and Responses: number of connections, time between start of connections;
	\item Connection: Number of request and responses per connection, applications modeling (HTTP, P2P, SMTP), transport protocols TCP/UDP based on the application, response sizes, request sizes, user think between exchanges on a connection;
	\item Packet: packet size (Maximum transmission unit), IP addresses, (MTU), bit rate and packet arrival distribution, 
	\item Link: link Latency Delay, loss rates.
\end{itemize}
Swing take as input collected \textit{pcap} files. Botta at al. \cite{do-you-trust} argues that due its complexity, they are rarely used to conduct experimental researchers. 
% Also, we can  justify due its overheads, since the performance of such complex traffic generator is limited\cite{legotg-paper}. The authors Vishwanat et al. \cite{swing-paper} cite that they have generated traces of about of 200 Mbps, about the same result found by \cite{legotg-paper}. In the other hand, D-ITG reached 9808 Mbps\cite{comparative-trafficgen-tools} in a link of 10 Gbps, but operating as a maximum throughput generator.

%> limitações dos traffic gen
Application level traffic generators may be realistic from a operation system perspective, but are not able to represent real complex scenarios. Replay engines such as  TCPreplay and TCPivo have some limitation. First, they usually do not replicate the same inter-packet times form the original trace, just creates a constant bandwidth traffic. They also requere storage of \textit{pcap} files, wich may become huge for  long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and limited sources.  Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen\cite{moongen-paper}. But all of them just offer a complet framework to be congfigured, but the customization of the traffic is all up to user to do. So, there is no simple way for the user to create an synthetic realistic traffic scenario.

%> low/high level APIs
We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. Many of the listed traffic generators provides their own high-level API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

@@

%> muitas ferramestas, mas dificil de gerar trafego realistico
Indeed, we have a large variety open-source tools available for custom traffic generation. But reproducing a realistic traffic scenario is a hard question. Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}. But usually this is not the goal of the project, so the researcher or the them have scarce time available to work over it. Since it is usually is not the main goal of the project, but just a mean many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.   Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation. Since it usually is not the goal of the research, but a mean.

%> Open source alternatives
For this gap tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration and provide a realistc traffic generaion. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-validation} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. This is clearly a hard task\cite{legotg-paper}, and an error prone activity. Again, we fall in the same problem a complex task that usually is not the goal of the project.

%> not automatic configuration
Another issue is the large variety of tools, and different methods of configuration and limitations. To create a custom traffic, a user must read large manuals, and custom-design scripts. One of our bigger proposals is create a tool able to automatically do this processes. So The user may design his custom traffic by creating his own Compact Trace Descriptor, and create a traffic using many different tools, like Ostinato, D-ITG, Iperf, but not caring about how to proper configure each of them.

@@

In this section we are going to present the SIMITAR architecture and operation. SIMITAR is composed of four components, as presented in the figure ~\ref{fig:architecture}:  the \textit{Sniffer}, a \textit{SQLite database}, the \textit{TraceAnalyzer}, and the \textit{FlowGenerator}. We explain each part down below.

\begin{figure}[ht!]
        \centering
        \includegraphics[width=\linewidth]{figures/architecture-diagram}
        \caption{Architecture of SIMITAR}
    \label{fig:architecture}
\end{figure}

@@

It has a data structure we developed called \textit{OrderedSet}. A set is a list of elements with no repetition but does not keep track of the insertion order. Our OrderedSet does. Also, it makes use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}. The listed header fields are inputs for a hash function, and its value is set on the ordered set which returns its order (index on the \textit{OrderedSet}). The index value is chosen as a packet \textit{flowID}.

@@

The database stores the collected raw data from the traces for further analysis. The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.  We choose an SQLite database, because according to its specifications it is simple and well-suitable for an amount of data smaller than terabytes \footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}. In the figure ~\ref{fig:simitar-database} we show the relational model of our database, which stores a set of features extracted from packets, along with the \textit{flowID} calculated by the sniffer component.

@@

At the \textbf{session layer}, we use a deterministic approach for evaluating file transference time and times between files: ON/OFF times sequence of packet trains. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-validation}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the ON times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Also in the case of just one packet, the ON time would be zero. So setting a minimum acceptable time to solve these issues. The OFF times, on the other hand, are defined by the constant \texttt{session\_cut\_time} \footnote{In the code it is called \texttt{DataProcessor::m\_session\_cut\_time} }. If the time between two packets of the same flow is larger than \texttt{session\_cut\_time}, we consider them belonging to a different file, so this time is a session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} for the \texttt{session\_cut\_time}: 30 seconds. The control of ON/OFF periods in the traffic generation is made by the \textit{Flow Generator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.

@@

\subsection{Flow Generator}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{figures/trace-flow}
	\caption{Class hierarchy of NetworkTrace and NetworkFlow, which enables the abstraction of the traffic generation model of the traffic generation engine.}
	\label{fig:network-trace-flow-class-diagram}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{figures/alg-simplified-harpoon}
	\caption{Simplified-harpoon emission algorithm}
	\label{fig:alg-simplified-harpoon}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{figures/alg-traffic-engine-config}
	\caption{Traffic engine configuration model}
	\label{fig:alg-traffic-engine-config}
\end{figure}

The Flow Generator handles the data on the \textit{Compact Trace Descriptor} file, and use to retrieve parameters for traffic generation. It crafts and controls each flow in a separated thread. We already implemented this component using Iperf traffic generator and Libtins C++ API, and it must follow the calss hierarcy as presented in the figure ~\ref{fig:network-trace-flow-class-diagram}.  This component was designed using the design pattern Factory, to simplify its expansion and support\footnote{If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow}, creating a new derived class (figure ~\ref{fig:network-trace-flow-class-diagram} ). On our current implementation we already have implemented \texttt{IperfFlow} and \texttt{TinsFlow}, and \texttt{DitgFlow} is under validation process. This new class has the requirement of not have any new attribute. The support for this new class must be given on the factory class \texttt{NetworkFlowFactory}. For closed loop packet-crafters (that means, tools which must establish a connection between the source and the destination), two methods must be implemented: \texttt{flowGenerate()} and \texttt{server()}. \texttt{flowGenerate()} is responsible for sending a \textit{file}, as defined on de figure~\ref{fig:modified-harpoon-model}, and \texttt{server()} to receive $n$ files. Open loop packet-crafters, such as we implemented using Libtins (just sent the packets, do not establishes a connection), the server do not need to be implemented.}.

This component and therefore our traffic generator is a multi-layer workload generator according to the typing introduced on chapter ~\ref{ch:literature-review} \footnote{Since it works both at packet and flow level, but do not work at application level.}. At the flow-level, SIMITAR controls each flow using the algorithm at figure~\ref{fig:alg-simplified-harpoon}. This algorithm handles our model defined at the figure ~\ref{fig:modified-harpoon-model}. This procedure is independent of the underlying packet crafting tool used. It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps for \texttt{start\_delay} seconds. This is the arrival time of the first flow packet. Passed this time, it then calls the underlying traffic generation tool(defined as command line argument), and pass to it the flowID, file ON time, number of packets and number of bytes to be sent (file size), and network interface. Then it sleeps the next session OFF time. When the list of ON/OFF times from the flow is over, the thread ends.

At the packet level, the job of our tool is to configure the underlying engine, to send a \textit{file}, as defined in the figure ~\ref{fig:modified-harpoon-model}. This method must use the available parameters, attributes and \textit{getters} to configure and generate a thread-safe traffic using the method \texttt{flowGenerate()}. The \textit{file} configuration must follow the in the figure ~\ref{fig:alg-traffic-engine-config}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Validation}\label{sec:validation}
